Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex
First typo-correction
Update correlated-sicm-and-srfm.tex
Second typo-correction

In the latter, the topography of a group of fixed HeLa has been investigated
by SICM (Fig.~\ref{fig:SICM_STED1}a) and, subsequently, the distribution of
the cytoskeletal protein actin was determined by confocal and STED microscopy
(Fig.~\ref{fig:SICM_STED1}b) on a second instrument. The area of the sample
imaged by both methods is marked in Fig.~\ref{fig:SICM_STED1}c (SICM: yellow
rectangle, STED: gray rectangle).

\begin{figure}	
  \centering
    \includegraphics[width=\textwidth]{gr/correlating/Hagemann2018-F4}
      \caption{
      \textbf{Correlative SICM and STED recording of a group of HeLa cells.} 
      \textbf{a:} Height (aa) and slope representatin (ab) of a SICM recording
      of HeLa cells. \textbf{b:} Confocal (ba) and STED (bb) recording of the
      region marked  
      with a black dotted line in a. \textbf{c:}  Relative position of 
      the SICM (yellow rectangle) and the confocal/STED (gray rectangle)
      images with respect to  each 
      other. \textbf{d:} Magnification of the STED (da), confocal  (db), SICM
      (dd) and slope (de) images. The magnified region is marked with a white 
      arrowhead in a and b. \textbf{df} and \textbf{dg} show an overlay of 
      the STED and the SICM data. 
      \textbf{Dc} shows the height profile along the white dotted line in dd.  Reprinted 
      with permission from Philipp Hagemann, Astrid Gesper, Patrick Happel: \emph{Correlative 
      stimulated emission depletion and scanning ion conductance microscopy.} ACS Nano 2018, 
      12, 5807-5815. Copyright 2018 American Chemical Society.}
  \label{fig:SICM_STED1}
\end{figure}

@@

% As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
% with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
% SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
% fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.

>>>>

In the latter, the topography of a group of fixed HeLa has been investigated
by SICM (Fig.~\ref{fig:SICM_STED1}a) and, subsequently, the distribution of
the cytoskeletal protein actin was determined by confocal and STED microscopy
(Fig.~\ref{fig:SICM_STED1}b) on a second instrument. The area of the sample
imaged by both methods is marked in Fig.~\ref{fig:SICM_STED1}c (SICM: yellow
rectangle, STED: grey rectangle).

\begin{figure}	
  \centering
    \includegraphics[width=\textwidth]{gr/correlating/Hagemann2018-F4}
      \caption{
      \textbf{Correlative SICM and STED recording of a group of HeLa cells.} 
      \textbf{a:} Height (aa) and slope representation (ab) of a SICM recording
      of HeLa cells. \textbf{b:} Confocal (ba) and STED (bb) recording of the
      region marked  
      with a black dotted line in a. \textbf{c:}  Relative position of 
      the SICM (yellow rectangle) and the confocal/STED (grey rectangle)
      images with respect to each 
      other. \textbf{d:} Magnification of the STED (da), confocal (db), SICM
      (dd) and slope (de) images. The magnified region is marked with a white 
      arrowhead in a and b. \textbf{df} and \textbf{dg} show an overlay of 
      the STED and the SICM data. 
      \textbf{Dc} shows the height profile along the white dotted line in dd.  Reprinted 
      with permission from Philipp Hagemann, Astrid Gesper, Patrick Happel: \emph{Correlative 
      stimulated emission depletion and scanning ion conductance microscopy.} ACS Nano 2018, 
      12, 5807-5815. Copyright 2018 American Chemical Society.}
  \label{fig:SICM_STED1}
\end{figure}

@@

% As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
% with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
% SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
% fluorescently labelled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
